IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-17 paper/formal.tex
more space savings in figures

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|erase il (fullconf id il' tS ie) =| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
|erasef il| is applied homomorphically.
Note that |erase il ie| is always equal to |ie| (and similar for |tS|)
in this simple setting.  However,
when the IFC language is extended with more constructs as shown in
Section~\ref{sec:extensions}, then this will no longer be the case.
\label{fig:erasure} }
\end{figure}

>>>>

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|erase il (fullconf id il' tS ie) =| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is the label of thread |id|}\\
    |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|  \qquad\qquad\qquad  |erase il emptyset = emptyset|
\end{align*}
\vspace*{-0.8cm}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
|erasef il| is applied homomorphically.
Note that |erase il ie| is always equal to |ie| (and similar for |tS|)
in this simple setting.  However,
when the IFC language is extended with more constructs as shown in
Section~\ref{sec:extensions}, then this will no longer be the case.
\label{fig:erasure} }
\end{figure}
